Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-14 paper.qmd
Updated Figure 15 label colour

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_tot_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  geom_rect(aes(xmin = 0.82, xmax = 0.92, ymin = 0.38, ymax = 0.58),
               fill = "transparent", color = "#000000", linewidth = 1) +
  geom_rect(aes(xmin = 0.9, xmax = 1, ymin = 1.25, ymax = 1.45),
               fill = "transparent", color = "#375cb1", linewidth = 1)  +
  geom_rect(aes(xmin = 0.35, xmax = 0.45, ymin = 0.55, ymax = 0.7),
               fill = "transparent", color = "#004616", linewidth = 1)  +
  geom_rect(aes(xmin = 0.7, xmax = 0.8, ymin = 0.25, ymax = 0.4),
               fill = "transparent", color = "#4c389a", linewidth = 1) +
  theme(legend.position = "none",
        plot.margin = margin(0, 0, 0, 0))
```

@@

right_top_img <- plot_digit_img(pixels_gathered_within, palette = "Blues 2", title_text = "(a)", hjust = 0.31) + theme(plot.margin = margin(0, 0, 0, 0))

@@

middle_img <- plot_digit_img(pixels_gathered_within, palette = "Greens 3", title_text = "(b)", hjust = 0.31) + theme(plot.margin = margin(0, 0, 0, 0))

@@

right_bottom_img <- plot_digit_img(pixels_gathered_within, palette = "Purples 2", title_text = "(c)", hjust = 0.31) + theme(plot.margin = margin(0, 0, 0, 0))

@@

imge_error_sample_outside <- plot_digit_img(pixels_gathered_outside, palette = "Grays", title_text = "(d)", hjust = 0.31) + theme(plot.margin = margin(0, 0, 0, 0))

##### inside
img_error_inside <- c(3179, 7363, 7650, 5241, 5173, 6981, 7228, 6673, 4636)

@@

imge_error_sample_inside <- plot_digit_img(pixels_gathered_inside, palette = "Oranges", title_text = "(e)", hjust = 0, ncol = 9) + theme(plot.margin = margin(0, 0, 0, 0))

@@

# Display the final combined plot
final_layout
```

>>>>

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_tot_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  geom_rect(aes(xmin = 0.82, xmax = 0.92, ymin = 0.38, ymax = 0.58),
               fill = "transparent", color = "#000000", linewidth = 1) +
  geom_rect(aes(xmin = 0.9, xmax = 1, ymin = 1.25, ymax = 1.45),
               fill = "transparent", color = "#375cb1", linewidth = 1)  +
  geom_rect(aes(xmin = 0.35, xmax = 0.45, ymin = 0.55, ymax = 0.7),
               fill = "transparent", color = "#004616", linewidth = 1)  +
  geom_rect(aes(xmin = 0.7, xmax = 0.8, ymin = 0.25, ymax = 0.4),
               fill = "transparent", color = "#4c389a", linewidth = 1) +
  theme(legend.position = "none",
        plot.margin = margin(0, 0, 0, 0),
        aspect.ratio = 1)
```

@@

right_top_img <- plot_digit_img(pixels_gathered_within, palette = "Blues 2", title_text = "a", hjust = 0.31) + theme(plot.margin = margin(0, 0, 0, 0))

@@

middle_img <- plot_digit_img(pixels_gathered_within, palette = "Greens 3", title_text = "b", hjust = 0.31) + theme(plot.margin = margin(0, 0, 0, 0))

@@

right_bottom_img <- plot_digit_img(pixels_gathered_within, palette = "Purples 2", title_text = "c", hjust = 0.31) + theme(plot.margin = margin(0, 0, 0, 0))

@@

imge_error_sample_outside <- plot_digit_img(pixels_gathered_outside, palette = "Grays", title_text = "d", hjust = 0.31) + theme(plot.margin = margin(0, 0, 0, 0))

##### inside
img_error_inside <- c(3179, 7363, 7650) #, 5241, 5173, 6981, 7228, 6673, 4636

@@

imge_error_sample_inside <- plot_digit_img(pixels_gathered_inside, palette = "Oranges", title_text = "e", hjust = 0, ncol = 9) + theme(plot.margin = margin(0, 0, 0, 0))

@@

# Display the final combined plot
#final_layout
full_layout/imge_error_sample_inside + plot_layout(widths = c(1, 1), 
                                                   heights = c(1, 0.2)) 
```
